NFL Draft Analysis

### 2020-05-10 draft_analysis.Rmd
Make this repository work with Github Pages - remove all of the qb clustering project work - collapse all of the code into the main directory

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(warn = -1)
library(tidyverse)
library(rvest)
library(gridExtra)
setwd("/Users/PhilipIpe/Documents/Data Science/Projects/NFL Analytics/Drafting")
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(warn = -1)
library(tidyverse)
library(rvest)
library(gridExtra)
setwd("/Users/PhilipIpe/Documents/Data Science/Projects/NFL Draft Analytics/")
```
